Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-08 article.tex
modifcation : used of environment cases

\DeclareMathOperator{\matcha}{MATCH}
\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

@@

\textbf{BASE :} \\
$LM(1,j)= \left\{ 
	\begin{array}{l l}

		MIN_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } & 
		\text{if $\stripe{\pmotif}{\first{1}}=\ustep$}\\
		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}&\\

		MAX_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
		\text{if $\stripe{\pmotif}{\first{1}}=\dstep$} \\
		\text{ $|\factor{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\

	\end{array} \right. $\\

\textbf{STEP :} \\
$LM(i,j)= \left\{ 
	\begin{array}{l l}

		MIN \{0\} \cup  I(i,j) & 
		\text{if $\stripe{\pmotif}{\first{i}}=\ustep$}\\

		MAX \{0\} \cup  D(i,j) & 
		\text{if $\stripe{\pmotif}{\first{i}}=\dstep$}\\

	\end{array} \right. $\\

@@

%$
%\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= 
%\begin{cases}
%true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$ with every element in $[\min,\max]$} \\
%false & otherwise
%\end{cases}
%$

$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\left\{ 
\begin{array}{l l}
	true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
		& \text{with every element in}\\ 
		&[\min,\max]\\

	false & otherwise\\
\end{array} \right.$\\

@@

\textbf{BASE :} \\
if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\	
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}	
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[j]<\max$}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
\\

if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\		
$ \PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
\\

if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[j]<\max$ and }\\
					&\text{$\ptext[j]$ is the maximal element}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}
= \left\{ 
		\begin{array}{l l}
			true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
					&\text{$\ptext[n_\ptext]$ is the maximal element}\\
			false 	& otherwise\\
		\end{array} \right. $\\	
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

\textbf{STEP :} \\		
$\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}= \\ \left\{ 
		\begin{array}{l l}

			\bigcup_{j<k}
			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
				& \text{if $\stripe{\pmotif}{i}=\ustep$
				and $i \notin \x$}\\
				& \text{and $i \notin \y$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

@@

			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
				&\text{and $i \in \x$ and $i \in \y$}\\ 
				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\	
			False & Otherwise\\																		
		\end{array} \right. $\\

@@

	\textbf{BASE :} \\
	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
				}\\
				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
	=$
	$ \max \left\{ 
			\begin{array}{l l}
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
				\\
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
				\\
				\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
			\end{array} \right. $\vspace{20pt}\\

	with
	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
				\begin{array}{l l}
					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
					 & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

>>>>

\DeclareMathOperator{\matcha}{M}
\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

@@

\textbf{BASE :} \\
$
LM(1,j)=
\begin{cases}
		MIN_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } & 
			\text{if $\stripe{\pmotif}{\first{1}}=\ustep$} \\
		\text{ $|\factor{1}| \leq LIS(j,j',\ptext[j'])  $}\}& \\
		&\\	
		MAX_{j<j'}\{0\} \cup \{\ptext[j'] |\text{ $j'$ such that \indent } &
			\text{if $\stripe{\pmotif}{\first{1}}=\dstep$} \\
		\text{ $|\factor{1}| \leq LDS(j,j',\ptext[j']) $}\}&\\			
\end{cases}
$

\textbf{STEP :} \\
$
LM(i,j)=
\begin{cases}
	MIN \{0\} \cup  I(i,j) & 
	\text{if $\stripe{\pmotif}{\first{i}}=\ustep$}\\
	MAX \{0\} \cup  D(i,j) & 
	\text{if $\stripe{\pmotif}{\first{i}}=\dstep$}\\		
\end{cases}
$

@@

$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
	true 	& \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
			& \text{with every element in}\\ 
			&[\min,\max]\\

	false 	& otherwise\\
\end{cases}
$

@@

\textbf{BASE :} \\
if $n_\pmotif \notin  \x $ and $n_\pmotif \notin  \y$ : \\	
$
\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j} =
\begin{cases}
	true 	& \text{if $\min<\ptext[j]<\max$}\\
	false 	& otherwise\\
\end{cases}
$
%$\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif+1}{j}= true $
\\

if $n_\pmotif \in  \x $ and $n_\pmotif \notin  \y$ : \\		
$
\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext} =
\begin{cases}
	true 	& \text{if $\min<\ptext[n_\ptext]<\max$}\\
	false 	& otherwise\\
\end{cases}
$
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $
\\

if $n_\pmotif \notin  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$
\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{j}=
\begin{cases}
	true 	& \text{if $\min<\ptext[j]<\max$ and }\\
			&\text{$\ptext[j]$ is the maximal element}\\
	false 	& otherwise\\
\end{cases}
$
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

if $n_\pmotif \in  \x$  and $n_\pmotif \in  \y$ and $\pmotif[n_\pmotif]$ is the maximal element: \\		
$
\PM{\pbmotif}{\ptext}{\min}{\max}{n_\pmotif}{n_\ptext}=
\begin{cases}
	true 	& \text{if $\min<\ptext[n_\ptext]<\max$and }\\
			&\text{$\ptext[n_\ptext]$ is the maximal element}\\
	false 	& otherwise\\
\end{cases}
$
%$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

\textbf{STEP :} \\		
$
\PM{\pbmotif}{\ptext}{\min}{\max}{i}{j}=
\begin{cases}
\bigcup_{j<k}
			\PM{\pbmotif}{\ptext}{\ptext[j]}{\max}{i+1}{k}
				& \text{if $\stripe{\pmotif}{i}=\ustep$
				and $i \notin \x$}\\
				& \text{and $i \notin \y$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

@@

			\PM{\pbmotif}{\ptext}{\min}{\ptext[j]}{i+1}{j+1} 
				& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
				&\text{and $i \in \x$ and $i \in \y$}\\ 
				&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
				& \text{and $\min<\ptext[j]<\max$} \\
			&\\

			False & Otherwise\\	
\end{cases}
$

@@

\textbf{BASE :} \\
$
\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} =
\begin{cases}
	1 & \text{if $\min_1=\pi_1[j]=\max_1$  
	}\\
	& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
	0 & otherwise\\
\end{cases}
$

@@

$
\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=max
\begin{cases}
	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
	\\
	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
	\\
	\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
\end{cases}
$

with \\
$
\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=
\begin{cases}
1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} 
	& \text{$\pi_1[i_1]<\min_1$ } \\
	& \text{and $\pi_2[i_2]<\min_2$} \\

1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
	& \text{$\pi_1[i_1]>\max_1$ } \\	
	&\text{and $\pi_2[i_2]>\max_2$}\\

0 	& \text{otherwise}\\	
\end{cases}
$
